Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}

### 2022-09-12 inst/skeleton/ms.Rmd
more cosmetic changes

Sims[[1]] %>% 
  group_by(lrscale) %>% 
  summarize(mean = mean(y), 
            lwr = quantile(y, .025), 
            upr = quantile(y, .975)) %>%
  ggplot(.,aes(factor(lrscale), y = mean, ymin=lwr, ymax=upr)) +
  theme_steve_web() +
  geom_pointrange() +
  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)") -> fig_sims

>>>>

QI[[1]] %>% 
  group_by(lrscale) %>% 
  summarize(mean = mean(y), 
            lwr = quantile(y, .025), 
            upr = quantile(y, .975)) %>%
  ggplot(.,aes(factor(lrscale), y = mean, ymin=lwr, ymax=upr)) +
  theme_steve_web() +
  geom_pointrange() +
  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)") -> fig_sims
